---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stmut

<!-- badges: start -->
<!-- badges: end -->

The goal of stmut is providing a series of functions to visualize which genes have somatic mutations in which spots when working on sptial transcriptomics data.



## Installation

You can install the development version of stmut from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("limin321/stmut")
```
## Instruction before using this package.
Have your data ready:


## Example

This is a basic example of how to run sptBClstRds function:

```{r example}
 library(stmut)
# ## basic example code
# files <- list.files(path = "./inst/extdata/spotIndex", pattern = ".txt", full.names = TRUE, recursive = FALSE)
# data1 <- read.csv("./inst/extdata/filtered_feature_bc.csv", header = TRUE)
# data2 <- read.csv("./inst/extdata/Graph-Based.csv", header = TRUE)
# path <- "./inst/extdata/tissue_positions_list.csv"
# df <- sptBClstRds(files=files,data1=data1, data2=data2, path=path)
# 
# head(df[[1]])
# head(df[[2]])
?sptBClstRds
```


An example on how to run sptMutCt()
```{r example2}
library(stmut)
index <- read.csv("./inst/extdata/spotBC.csv", header = TRUE)
files2 <- list.files(path = "./inst/extdata/mpileup",pattern = "MpileupOutput_RNA.txt", full.names = TRUE, recursive = TRUE, include.dirs = TRUE)
df1 <- sptMutCt(index = index, files = files2)

head(df1[[1]])
head(df1[[2]])


```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:




In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
